Draft_Mid_Term

### 2022-10-03 Draft_Mid_Term.Rmd
10/03 update
knn added

#Zipcode:
zipcode<-st_read('./data/zipcode/Zipcode.shp')
zipcode<-zipcode %>% st_transform(crs=4326) %>% rename(shapeLeng = shape_Leng,shapeArea = shape_Area) %>% dplyr::select(zip,po_name,shapeLeng,shapeArea)

#Capital Improvement Projects:
investment<-st_read('./data/Capital_Improvement_Projects/Capital_Improvement_Projects.shp')
investment<-investment %>% st_transform(crs=4326)

#Business Investment Opportunity Zones:
business_invest<-st_read('./data/Business/Business_Investment_Opportunity_Zones.shp')
business_invest<-business_invest %>% st_transform(crs=4326)

#Park Locations:
park<-st_read('./data/Park_Locations/Park_Locations.shp')
park<-park %>% st_transform(crs=4326)
```

```{r neighborhood_effects_factor_and_clean}
#spatial features collection

#Crime:
crime<-st_read('./data/Crime - Violent.geojson')
crime<-crime %>% st_transform(crs=4326)
crime1<-crime %>% mutate(crime_sum = X2019.raw+X2020.raw+X2021.raw) %>%  dplyr::select(crime_sum)

#Long Commute:
long_commute<-st_read('./data/LongCommute.geojson')
long_commute<-long_commute %>% st_transform(crs=4326) %>% mutate(PctLongCommute = X2020) %>%  dplyr::select(PctLongCommute)

#Percent of Grocery:
grocery<-st_read('./data/Proximity to a Grocery Store.geojson')
Pctgrocery<-grocery %>% st_transform(crs=4326) %>% mutate(Pctgrocery = X2021) %>%  dplyr::select(Pctgrocery)

#Percent of canopy in residential area:
canopy<-st_read('./data/Tree Canopy - Residential.geojson')
Pctcanopy<-canopy %>% st_transform(crs=4326) %>% mutate(Pctcanopy = X2012) %>% dplyr::select(Pctcanopy)

#Percent of Test Proficiency in Elementary Schools:
test_elementary<-st_read('./data/Test Proficiency - Elementary School.geojson')
Pcttest1<-test_elementary%>% st_transform(crs=4326) %>%mutate( test.elementary = X2019) %>% dplyr::select(test.elementary)

#Percent of Test Proficiency in Middle Schools:
test_middle<-st_read('./data/Test Proficiency - Middle School.geojson')
Pcttest2<-test_middle%>% st_transform(crs=4326) %>%mutate( test.middle = X2019) %>% dplyr::select(test.middle)

#Percent of Test Proficiency in High Schools:
test_high<-st_read('./data/Test Proficiency - High School.geojson')
Pcttest3<-test_high%>% st_transform(crs=4326) %>% mutate(test.high = X2019) %>% dplyr::select(test.high)

#Percent of Bachelor's Degree:
bachelor<-st_read('./data/Education Level - Bachelor Degree.geojson')
PctBachelor<-bachelor %>% st_transform(crs=4326) %>% mutate(PctBachelor = X2020) %>% dplyr::select(PctBachelor)

#Median Age of Residents:
age<-st_read('./data/Age of Residents.geojson')
MedAge<-age %>% st_transform(crs=4326) %>% mutate(MedAge = X2020) %>% dplyr::select(MedAge)
```

@@

@@

ggcorrplot(
  round(cor(numericVars), 1), 
  p.mat = cor_pmat(numericVars),
  colors = c("#0571b0", "#ffffff", "#ca0020"),
  type="lower",
  insig = "blank") +  
    labs(title = "Correlation across numeric variables") 
```

>>>>

#Zipcode:
##用于neighborhood effects分析
zipcode<-st_read('./data/zipcode/Zipcode.shp')
zipcode<-zipcode %>% st_transform(crs=4326) %>% rename(shapeLeng = shape_Leng,shapeArea = shape_Area) %>% dplyr::select(zip,po_name,shapeLeng,shapeArea)
```

```{r}
ggplot()+
  geom_sf(data=st_union(zipcode))+
  geom_sf(data=park_amenities.sf)
```

```{r}
ggplot()+
  geom_sf(data=st_union(tract))+
  geom_sf(data=park_easement.sf)
```

```{r amenity_facility_feature,warning=FALSE}
#1.college:
college<-st_read('./data/college/Colleges.shp')
college.sf<-college %>% st_transform(crs = 4326) %>% dplyr::select(geometry) %>% na.omit() 
#2.daycare:
daycare<-st_read('./data/daycare/Daycare.shp')
daycare.sf<-daycare %>% st_transform(crs=4326)%>% dplyr::select(geometry) %>% na.omit()

#3.Medical Facilities:
MedicalFacilities<-st_read('./data/medical/MedicalFacilities.shp')
MedicalFacilities.sf<-MedicalFacilities %>% st_transform(crs=4326)%>% dplyr::select(geometry) %>% na.omit()

#4.library:
## 数目不太多
library<-st_read('./data/library/Library.shp')
library.sf<-library %>% st_transform(crs=4326)%>% dplyr::select(geometry) %>% na.omit()

#5.Historical cemeteries:
## 原始数据是polygon,为了方便计算，使用st_centroid取了每个polygon的质心
hist_cemeteries<-st_read('./data/historic_cemeteries/Historic_Cemeteries.shp')
hist_cemeteries.sf<-hist_cemeteries %>% st_transform(crs=4326)%>% st_centroid() %>% dplyr::select(geometry) %>% na.omit()

#6.Historical Properties:
## 原始数据是polygon,为了方便计算，使用st_centroid取了每个polygon的质心
hist_properties<-st_read('./data/historic_properties/HistoricProperty_National.shp')
hist_properties.sf<-hist_properties%>% st_transform(crs=4326)%>%st_centroid() %>% dplyr::select(geometry) %>% na.omit()

#7.church
## 数目非常多
church<-st_read('./data/church/Churches.shp')
church.sf<-church %>% st_transform(crs=4326)%>% dplyr::select(geometry) %>% na.omit()

#8.park_amenities:
park_amenities<-st_read('./data/park_amenities/ParkAmenity.shp')
park_amenities.sf<-park_amenities%>% st_transform(crs=4326)%>% dplyr::select(geometry) %>% na.omit()

#9.park easement:
park_easement<-st_read('./data/park_easement/ParkEasements.shp')
park_easement.sf<-park_easement%>% st_transform(crs=4326)%>%st_centroid() %>% dplyr::select(geometry) %>% na.omit()

#10.Capital Improvement Projects:
capital_improve<-st_read('./data/Capital_Improvement_Projects/Capital_Improvement_Projects.shp')
capital_improve.sf<-capital_improve %>% st_transform(crs=4326)%>% dplyr::select(geometry) %>% na.omit()

#11.Business Investment Opportunity Zones:
##这个=做binary指标。原始数据是polygon;考虑使用buffer?
business_invest<-st_read('./data/Business/Business_Investment_Opportunity_Zones.shp')
business_invest<-business_invest %>% st_transform(crs=4326)
```

```{r neighborhood_effects_factor_and_clean}
#spatial features collection
##这个chunk内的都是以census tract为单位的指标；将合并到data

#1.Crime:
crime<-st_read('./data/Crime - Violent.geojson')
crime<-crime %>% st_transform(crs=4326)
crime1<-crime %>% mutate(crime_sum = X2019.raw+X2020.raw+X2021.raw) %>%  dplyr::select(crime_sum)

#2.Long Commute:
long_commute<-st_read('./data/LongCommute.geojson')
long_commute<-long_commute %>% st_transform(crs=4326) %>% mutate(PctLongCommute = X2020) %>%  dplyr::select(PctLongCommute)

#3.Percent of Grocery:
grocery<-st_read('./data/Proximity to a Grocery Store.geojson')
Pctgrocery<-grocery %>% st_transform(crs=4326) %>% mutate(Pctgrocery = X2021) %>%  dplyr::select(Pctgrocery)

#4.Percent of canopy in residential area:
canopy<-st_read('./data/Tree Canopy - Residential.geojson')
Pctcanopy<-canopy %>% st_transform(crs=4326) %>% mutate(Pctcanopy = X2012) %>% dplyr::select(Pctcanopy)

#5.Percent of Test Proficiency in Elementary Schools:
test_elementary<-st_read('./data/Test Proficiency - Elementary School.geojson')
Pcttest1<-test_elementary%>% st_transform(crs=4326) %>%mutate( test.elementary = X2019) %>% dplyr::select(test.elementary)

#6.Percent of Test Proficiency in Middle Schools:
test_middle<-st_read('./data/Test Proficiency - Middle School.geojson')
Pcttest2<-test_middle%>% st_transform(crs=4326) %>%mutate( test.middle = X2019) %>% dplyr::select(test.middle)

#7.Percent of Test Proficiency in High Schools:
test_high<-st_read('./data/Test Proficiency - High School.geojson')
Pcttest3<-test_high%>% st_transform(crs=4326) %>% mutate(test.high = X2019) %>% dplyr::select(test.high)

#8.Percent of Bachelor's Degree:
bachelor<-st_read('./data/Education Level - Bachelor Degree.geojson')
PctBachelor<-bachelor %>% st_transform(crs=4326) %>% mutate(PctBachelor = X2020) %>% dplyr::select(PctBachelor)

#9.Median Age of Residents:
age<-st_read('./data/Age of Residents.geojson')
MedAge<-age %>% st_transform(crs=4326) %>% mutate(MedAge = X2020) %>% dplyr::select(MedAge)
```

@@

```{r knn}
st_c<-st_coordinates

#1.college:
data <-
  data %>% 
  mutate(
    college_nn1 = nn_function(st_c(data),st_c(college.sf), 1),
    college_nn2 = nn_function(st_c(data),st_c(college.sf), 2),
    college_nn3 = nn_function(st_c(data),st_c(college.sf), 3),
    college_nn4 = nn_function(st_c(data),st_c(college.sf), 4),
    college_nn5 = nn_function(st_c(data),st_c(college.sf), 5),
    )

#2.daycare:
data <-
  data %>% 
  mutate(
    daycare_nn1 = nn_function(st_c(data),st_c(daycare.sf), 1),
    daycare_nn2 = nn_function(st_c(data),st_c(daycare.sf), 2),
    daycare_nn3 = nn_function(st_c(data),st_c(daycare.sf), 3),
    daycare_nn4 = nn_function(st_c(data),st_c(daycare.sf), 4),
    daycare_nn5 = nn_function(st_c(data),st_c(daycare.sf), 5),
    )

#3.Medical Facilities:
data <-
  data %>% 
  mutate(
    MedicalFacilities_nn1 = nn_function(st_c(data),st_c(MedicalFacilities.sf), 1),
    MedicalFacilities_nn2 = nn_function(st_c(data),st_c(MedicalFacilities.sf), 2),
    MedicalFacilities_nn3 = nn_function(st_c(data),st_c(MedicalFacilities.sf), 3),
    MedicalFacilities_nn4 = nn_function(st_c(data),st_c(MedicalFacilities.sf), 4),
    MedicalFacilities_nn5 = nn_function(st_c(data),st_c(MedicalFacilities.sf), 5),
    )

#4.library:
data <-
  data %>% 
  mutate(
    library_nn1 = nn_function(st_c(data),st_c(library.sf), 1),
    library_nn2 = nn_function(st_c(data),st_c(library.sf), 2),
    library_nn3 = nn_function(st_c(data),st_c(library.sf), 3),
    library_nn4 = nn_function(st_c(data),st_c(library.sf), 4),
    library_nn5 = nn_function(st_c(data),st_c(library.sf), 5),
    )

#5.Historical cemeteries:
data <-
  data %>% 
  mutate(
    hist_cemeteries_nn1 = nn_function(st_c(data),st_c(hist_cemeteries.sf), 1),
    hist_cemeteries_nn2 = nn_function(st_c(data),st_c(hist_cemeteries.sf), 2),
    hist_cemeteries_nn3 = nn_function(st_c(data),st_c(hist_cemeteries.sf), 3),
    hist_cemeteries_nn4 = nn_function(st_c(data),st_c(hist_cemeteries.sf), 4),
    hist_cemeteries_nn5 = nn_function(st_c(data),st_c(hist_cemeteries.sf), 5),
    )

#6.Historical Properties:
data <-
  data %>% 
  mutate(
    hist_properties_nn1 = nn_function(st_c(data),st_c(hist_properties.sf), 1),
    hist_properties_nn2 = nn_function(st_c(data),st_c(hist_properties.sf), 2),
    hist_properties_nn3 = nn_function(st_c(data),st_c(hist_properties.sf), 3),
    hist_properties_nn4 = nn_function(st_c(data),st_c(hist_properties.sf), 4),
    hist_properties_nn5 = nn_function(st_c(data),st_c(hist_properties.sf), 5),
    )

#7.church
data <-
  data %>% 
  mutate(
    church_nn1 = nn_function(st_c(data),st_c(church.sf), 1),
    church_nn2 = nn_function(st_c(data),st_c(church.sf), 2),
    church_nn3 = nn_function(st_c(data),st_c(church.sf), 3),
    church_nn4 = nn_function(st_c(data),st_c(church.sf), 4),
    church_nn5 = nn_function(st_c(data),st_c(church.sf), 5),
    )

#9.park easement:
data <-
  data %>% 
  mutate(
    park_easement_nn1 = nn_function(st_c(data),st_c(park_easement.sf), 1),
    park_easement_nn2 = nn_function(st_c(data),st_c(park_easement.sf), 2),
    park_easement_nn3 = nn_function(st_c(data),st_c(park_easement.sf), 3),
    park_easement_nn4 = nn_function(st_c(data),st_c(park_easement.sf), 4),
    park_easement_nn5 = nn_function(st_c(data),st_c(park_easement.sf), 5),
    )

#10.Capital Improvement Projects:
data <-
  data %>% 
  mutate(
    capital_improve_nn1 = nn_function(st_c(data),st_c(capital_improve.sf), 1),
    capital_improve_nn2 = nn_function(st_c(data),st_c(capital_improve.sf), 2),
    capital_improve_nn3 = nn_function(st_c(data),st_c(capital_improve.sf), 3),
    capital_improve_nn4 = nn_function(st_c(data),st_c(capital_improve.sf), 4),
    capital_improve_nn5 = nn_function(st_c(data),st_c(capital_improve.sf), 5),
    )
```

```{r eval=FALSE}
#8.park_amenities:
###这个需要将三围点变成二维点
data0 <-
  data0 %>% 
  mutate(
    park_amenities_nn1 = nn_function(st_c(data0),st_c(park_amenities.sf), 1),
    park_amenities_nn2 = nn_function(st_c(data0),st_c(park_amenities.sf), 2),
    park_amenities_nn3 = nn_function(st_c(data0),st_c(park_amenities.sf), 3),
    park_amenities_nn4 = nn_function(st_c(data0),st_c(park_amenities.sf), 4),
    park_amenities_nn5 = nn_function(st_c(data0),st_c(park_amenities.sf), 5),
    )
```

@@

ggcorrplot(
  round(cor(numericVars), 1), 
  p.mat = cor_pmat(numericVars),
  colors = c("#0571b0", "#ffffff", "#ca0020"),
  type="lower",
  insig = "pch") +  
    labs(title = "Correlation across numeric variables")+plotTheme()
```
```{r summary_amenities_feature}
amenities_feature.list<-data %>% dplyr::select(starts_with('daycare_'),starts_with('MedicalFacilities_'),starts_with('hist_c'),starts_with('park_'),starts_with('capital_'),starts_with('Pct'),starts_with('test.e'),pctTotalVacant, pctRenterOccupied, pctWhite,pctPoverty,MedRent ,MedHHInc,MedAge) %>% st_drop_geometry()

#stargazer:
stargazer(amenities_feature.list, type = "html", 
          title = "Table DATA 2.1 Summary Statistics of Internal Characteristics ",
          header = FALSE,
          single.row = TRUE)
```

```{r amenities_feature_matrix}
numericVars2 <- 
  select_if(amenities_feature.list, is.numeric) %>% na.omit()

ggcorrplot(
  round(cor(numericVars2), 1), 
  p.mat = cor_pmat(numericVars2),
  colors = c("#0571b0", "#ffffff", "#ca0020"),
  type="lower",
  insig = "pch") +  
    labs(title = "Correlation across numeric variables")+plotTheme()
```
